\TheTitle

### 2016-09-18 linvis.tex

If the user is searching by commit ID, the ID can be specified by using any of its unique prefixes. For example, the commit
\mycode{c267548755a184ef97301071300c1739a564e135} is returned when the user searches for a
commit ID of \mycode{c26} in the 3.10 Linux kernel. % This commit is a non-merge commit
% performed in one of the largest merge-trees of the kernel; however, this feature
% will work with any commit ID.

@@

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/list_tree.png}
        \caption{List tree view of merge 73287a43cc79ca06629a88d1a199cd283f42456a}
        \label{fig:list_tree}
\end{figure}

@@

The Reingold-Tilford tree\cite{Reingold1981} (Figures \ref{fig:zoomed_tree} and
\ref{fig:tree}) allows the visualization and navigation of the entire merge-tree in
an intuitive representation of the tree.  This illustrates a clear notion of root
and leaves, and how to navigate in either direction. Some of the merge trees are
very large (Figure~\ref{fig:zoomed_tree}), containing thousands of commits and
merges. While the tree is capable of producing a visualization, it becomes much more
difficult to understand. For example the merge
73287a43cc79ca06629a88d1a199cd283f42456a performed by Linus Torvalds in May 1, 2013,
merged 1722 non-merge commits and 91 merges. \footnote{
        This commit can be inspected at
        \url{http://li.turingmachine.org/commits/73287a43cc79ca06629a88d1a199cd283f42456a}}

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/tree_zoom.png}
        \caption{The complete Reingold-Tilford tree of a merge by Linus
          (73287a43cc79ca06629a88d1a199cd283f42456a) containing 1722 non-merge
          commits touching 239 modules and 1525 files.}
        \label{fig:zoomed_tree}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/tree_view.png}
        \caption{Detail of the Reingold-Tilford Tree in Figure~\ref{fig:zoomed_tree}.}
        \label{fig:tree}
\end{figure}

The tree can be displayed with some merges nodes collapsed, hence
showing only parts of the tree that are of interest to the user. Furthermore, the user can
zoom the tree by scrolling the mouse wheel to see more of the topology of the tree,
or to see the details of a given part of the tree.

@@

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/bubble_tree.pdf}
        \caption{Bubble Tree of merge 73287a43cc79ca06629a88d1a199cd283f42456a,
                showing in red (the tiny dot close to the middle) the location of
                the commit highlighted in Figure~\ref{fig:zoomed_tree}.}
        \label{fig:bubble_tree}
\end{figure}

@@

\begin{figure*}
        \centering
        \includegraphics[width=0.97\textwidth]{figures/042dd_tree.png}
        \caption{Merge tree topology for the same merge as in
                Figure~\ref{fig:dag_view}.}
        \label{fig:tree_view}
\end{figure*}

>>>>

If the user is searching by commit ID, the ID can be specified by using any of its unique prefixes. For example, the commit
\mycode{3f17ea6dea8ba5668873afa54628a91aaa3fb1c0} is returned when the user searches for a
commit ID of \mycode{3f17e} in the 3.16 Linux kernel.

@@

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/list_tree.png}
        \caption{List tree view of merge 3f17ea6}
        \label{fig:list_tree}
\end{figure}

@@

The Reingold-Tilford tree\cite{Reingold1981} (Figures \ref{fig:reingold_tree} and
\ref{fig:reingold_tree_zoom}) allows the visualization and navigation of the entire merge-tree in
an intuitive representation of the tree.  This illustrates a clear notion of root
and leaves, and how to navigate in either direction. Some merge trees are very
large, containing thousands of commits and merged. While the tree is capable of
producing a visualization, it becomes far more difficult to understand. For example,
the merge, 3f17ea6 performed by Linus Torvalds June 8 2014, contains 7217 commits
and merges. \footnote{This commit can be inspected at
  \url{http://li.turingmachine/org/commits/3f17ea6dea8ba5668873afa54628a91aaa3fb1c0}}

      \begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/4dc4_tree.pdf}
        \caption{Merge 4dc4226 is a subtree of 3f17ea6, for the power-management
          module of the kernel}
        \label{fig:reingold_tree}
      \end{figure}

      \begin{figure*}
        \centering
        \includegraphics[width=0.98\textwidth]{figures/4dc4_zoom_tree.pdf}
        \caption{Zoomed out view of the Reingold-Tilford tree for merge 4dc4226}
        \label{fig:reingold_tree_zoom}
      \end{figure*}

      The user is initially greeted with their current node centered on the screen.
      They are able to zoom the tree by scrolling the mouse, and clicking and
      dragging to pan the tree. They can see more details about a node by clicking
      on it, which will provide them a link to the specific page for that commit.

@@

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/bubble_tree.pdf}
        \caption{Bubble Tree of merge 3f17ea6, merge 4dc4226 is the currently
          selected merge and is highlighted in orange.}
        \label{fig:bubble_tree}
\end{figure}

@@

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/042dd_tree.pdf}
        \caption{Merge tree topology for the same merge as in
                Figure~\ref{fig:dag_view}.}
        \label{fig:tree_view}
\end{figure}
